---
title: "Rows to Columns"
author: "Elliot Hershberg"
date: "9/23/2021"
output: html_document
---

```{r imports, warning=FALSE}
library(tidyverse)
```

Let's say I want data of the following shape:

```{r create example data}
example <- tribble(
  ~gene, ~time0h, ~time1h, ~time3h, ~time4h,
  "ASS", 4.12, 5.2, 3.4, 3.2,
  "BAS", 1.2, 3.4, 4.6, 3.8,
  "CAS", 10.2, 2.3, 0.8, 0.1
  
)

example
```

(Example from [Mfuzz](http://mfuzz.sysbiolab.eu/))

To start I have the following shape:

```{r create actual data}
df <- tribble(
  ~time, ~ASS, ~BAS, ~CAS,
  "time0h", 4.12, 1.2, 10.2,
  "time1h", 5.2, 3.4, 2.3,
  "time3h", 3.4, 4.6, 0.8,
  "time4h", 3.2, 3.8, 0.1
)

df
```

So I want to transpose the dataframe, since my rows are what I want my columns to be:

```{r}
t(df)
```

While the code is simple, it creates a character vector:

```{r}
typeof(t(df))
```

And I have to do some manual clean up when converting back to a tibble as a result:

```{r}
reshaped <- df %>%
  select(!time) %>%
  t() %>%
  as_tibble(.name_repair = "minimal")

colnames(reshaped) <- df$time
reshaped$gene <- colnames(df)[2:ncol(df)]

reshaped <- reshaped %>%
  relocate(gene)

reshaped
```

It feels like I should be able to do a transpose without getting the wonky intermediate character vector, but couldn't find a simple solution with either `pivot_*` from `{tidyr}`.



